Erosion of somatic tissue identity with loss of the X-linked intellectual disability factor KDM5C

### 2024-07-25 submission/manuscript.Rmd
move icc to its own section

## Cell culture
We utilized our previously established cultures of male wild-type and _Kdm5c_ mutant embryonic stem cells[@samantaActivationXistEvolutionarily2022]. Sex was confirmed by genotyping _Uba1_ on the X and Y chromosomes with the following primers: 5'-TGGATGGTGTGGCCAATG-3', 5'-CACCTGCACGTTGCCCTT-3'. Deletion of _Kdm5c_ was confirmed through the primers 5'-ATGCCCATATTAAGAGTCCCTG-3', 5'-TCTGCCTTGATGGGACTGTT-3', and 5'-GGTTCTCAACACTCACATAGTG-3'.

@@

Immunocytochemistry of DAZL in EpiLCs was performed by washing cells thrice with phosphobuffered saline (PBS), fixing cells in 4% paraformaldehyde, washing thrice in PBS, blocking in PBS containing 0.3% Triton X-100, and 5% fetal bovine serum for 1 hour, washing thrice with PBS, and incubating in primary antibody (Rabbit anti DAZL, abcam ab34139, 1:200) in the blocking solution overnight at 4C. The next day cells were rinsed thrice with PBS, incubated in secondary antibody (Alexafluor 488 Invitrogen #710369, 1:1000) in blocking buffer, rinsed thrice in PBS, and then imaged. Images were taken blinded for genotype, chosen based on similar levels of DAPI signal, and then quantified via ImageJ.

>>>>

## Cell culture
We utilized our previously established cultures of male wild-type and _Kdm5c_ knockout (-KO) embryonic stem cells[@samantaActivationXistEvolutionarily2022]. Sex was confirmed by genotyping _Uba1_ on the X and Y chromosomes with the following primers: 5'-TGGATGGTGTGGCCAATG-3', 5'-CACCTGCACGTTGCCCTT-3'. Deletion of _Kdm5c_ was confirmed through the primers 5'-ATGCCCATATTAAGAGTCCCTG-3', 5'-TCTGCCTTGATGGGACTGTT-3', and 5'-GGTTCTCAACACTCACATAGTG-3'.

@@

## Immunocytochemistry (ICC)
ICC of DAZL in EpiLCs was performed by washing cells thrice with phosphobuffered saline (PBS), fixing cells in 4% paraformaldehyde, washing thrice in PBS, blocking in PBS containing 0.3% Triton X-100, and 5% fetal bovine serum for 1 hour, washing thrice with PBS, and incubating in primary antibody (Rabbit anti DAZL, abcam ab34139, 1:200) in the blocking solution overnight at 4C. The next day cells were rinsed thrice with PBS, incubated in secondary antibody (Alexafluor 488 Invitrogen #710369, 1:1000) in blocking buffer, rinsed thrice in PBS, and then imaged. Images were taken blinded for genotype, chosen based on similar levels of DAPI signal, and then quantified via ImageJ.
